Interactive web-based flood modeling at country wide scale and planter size resolution.

### 2014-06-27 article.tex
fix bib and full names

\author{\underline{F. Baart}
  \address[A1]{\it{Deltares,
      Rotterdamseweg,
      Delft, The Netherlands (fedor.baart@deltares.nl, arthur.vandam@deltares.nl, gennadii.donchyts@deltares.nl)}},
  K. K. Ha
  \address[B1]{\it{Nelen \& Schuurmans,
      Zakkendragerssteeg,
      Utrecht, The Netherlands (jack.ha@nelen-schuurmans.nl, martijn.siemerink@nelen-schuurmans.nl)}},
  A. van Dam \addressmark[A1],
  G. Donchyts \addressmark[A1],
  M. Siemerink \addressmark[B1]
}

>>>>

\author{\underline{Fedor Baart}
  \address[A1]{\it{Deltares,
      Rotterdamseweg,
      Delft, The Netherlands (fedor.baart@deltares.nl, arthur.vandam@deltares.nl, gennadii.donchyts@deltares.nl)}},
  Jack Ha
  \address[B1]{\it{Nelen \& Schuurmans,
      Zakkendragerssteeg,
      Utrecht, The Netherlands (jack.ha@nelen-schuurmans.nl, martijn.siemerink@nelen-schuurmans.nl)}},
  Arthur van Dam \addressmark[A1],
  Gennadii Donchyts \addressmark[A1],
  Martijn Siemerink \addressmark[B1]
}
